I am grateful to many people who have helped me through my academic journey. First, Paul Diehl has been a truly outstanding advisor. He has been an excellent teacher and mentor who dramatically improved my ability to think clearly about armed conflict, consistently pushed me to improve my work, and conferred on me a tremendous amount of knowledge about teaching, publishing, and countless other professional skills. His absurdly prompt feedback and advice were especially welcome in the past year as I completed this dissertation and navigated the job market.

The other members of my dissertation committee were invaluable as well. John Vasquez taught me a great deal about theorizing and thinking scientifically about international relations, and has been incredibly supportive throughout my time at Illinois. Brian Gaines brought much-needed methodological expertise and attention to detail to the committee. Carol Leff was a late addition to the committee, but provided many excellent insights regarding ethnic politics and the qualitative case studies. 

I also benefited from the teaching, advice, and support of numerous other faculty and staff members at Illinois. Bob Pahre served on the committee at the prospectus stage and consistently provided a unique and useful prospective on my work. Xinyuan Dai was enthusiastically supportive while I completed my coursework and exams, and Jim Kuklinski's research design class stands out as a highlight of that portion of my career. I began exploring an early version of the idea for this dissertation while a Schroeder Fellow at the Cline Center for Advanced Social Research. I am thus grateful to the Schroeder brothers for funding the position, and to Pete Nardulli and Scott Althaus for their valuable work at the Cline Center. Maryalice Wu provided me with a year of funding and the opportunity to refine my methodological skills at the Center for Innovation in Teaching and Learning. Finally, Brenda Stamm is surely one of the most talented and dedicated administrators at the University of Illinois, and I am grateful for all her help over the years in navigating departmental and university procedures.

I was extremely fortunate to go through the PhD program with a wonderful group of fellow students from whom I learned a great deal, and who also provided excellent companionship along the way. Watching basketball with Paul Testa and Kyle Estes was the best occasional distraction from political science anyone could ask for, and coffee klatch with Gina Reynolds, Tarah Williams, and a rotating cast of others was always a highlight of my week. There were many others with whom I greatly enjoyed spending time, including Kaye Usry, Jason Renn, Ashly Townsen, Bryce Reeder, Todd Robinson, Matt Powers, Tyler Pack, Blair Niece, Gina Martinez, Matt Spears, Bryce Dietrich, and Ashlea Rundlett. I have undoubtedly forgotten many more, and for that I apologize.

Lastly, none of this would have been possible without the support of my family. My parents, Ann and Bob, financed my undergraduate eduction. They and my grandmother, Alice Bowden, provided me with frequent financial help through my time as a graduate student. More importantly, they always regarded pursuing a PhD as a normal thing to do with one's life, and were incredibly encouraging every step of the way. Thank you all.