## Research Design

### The Afrobarometer Survey

To examine the relationship between repression and individual attitudes toward political participation and ethnic identities, I use waves 3-6^[The ethnic vs. national identity question was not asked in waves 1 and 2.] of the Afrobarometer survey. The Afrobarometer is administered by researchers at Michigan State University, the Institute for Democracy in South Africa, and the Center for Democratic Development in Ghana. In each wave the survey attempts to obtain a nationally-representative sample of 20-25 African countries. This is accomplished by randomly sampling geographic areas (villages, neighborhoods, etc), with selection probabilities weighted by population. Within each geographic area a starting point is chosen at random, from which interviews begin randomly selecting households. Individuals are then randomly selected within households, alternating between men and women to ensure gender balance. The sample in each country usually numbers either 1,200 or 2,400, depending on the size and diversity of the country. Respondents are asked over 300 questions on their demographics and background, and their opinions on a wide range of political and cultural questions. One advantage of using such a general survey is the relatively low likelihood that individuals will be primed to answer questions about ethnicity in a way that is not representative of their normal opinions [@Eifert2010].

Attributes for each survey wave are summarized in Table \@ref(tab:afro-topline). The four waves span the period 2005--2016, cover 38 countries, and collect a total of 158,362 individual responses. Response rates are generally quite high, averaging 76.5% in wave 6, and 77.7% in wave 5. A detailed summary of included countries is provided in Table \@ref(tab:response) of the Appendix.

Wave  | Years  | Total Responses  | Countries
--|---|---|--
 3 | 2005 | 25,397 | 18
 4 | 2008 | 27,713 | 20
 5 | 2011--2013 | 51,587 | 34
 6 | 2016 | 53,935 | 36
 Total | 2005--2016 | 158,362 | 36
 Table: (\#tab:afro-topline) The Afrobarometer Survey by Wave

One concern relevant to the present application is that in rare cases the Afrobarometer excludes geographic areas experiencing significant violence or other factors that would pose a danger to interviewers. Additionally, questions about ethnic identity are not asked in some countries where doing so is deemed to be potentially harmful to the sampled communities. Each of these attributes is suboptimal, but I argue that each introduces bias *against* my hypotheses, rather than for them. I expect that repression will induce individuals to be more willing to engage in violent mobilization, and more likely to identify with their ethnic group. By excluding areas experiencing high levels of violence, the sample is likely to exclude many of the areas experiencing the highest levels of repression. Thus, my hypotheses face a hard test --- I must find an effect for repression in a sample where repression levels are mostly low or moderate.

### Dependent Variables

#### Ethnic Identity {-}

The first dependent variable explored in this chapter is *ethnic identification*. The Afrobarometer asks individuals about the extent to which they identify with their ethnic group, relative to their nation. The question text is as follows:

>"Let us suppose that you had to choose between being a [ENTER NATIONALITY] and being a ________ [Respondent’s Ethnic Group]. Which of the following best expresses your feelings?" 

Respondents place themselves on a five point scale with the possible responses: "I feel only [ethnicity]", "I feel more [ethnicity] than [nationality]", "I feel equally [ethnicity] and [nationality]", "I feel more [nationality] than [ethnicity]", and "I feel only [nationality]". In most models I collapse the measure into a binary variable, with respondents in the first two categories coded as ethnic identifiers, and all others as non-ethnic identifiers.

Individuals self-report their ethnicity earlier in the survey. The question is open-ended, allowing for the possibility that respondents may conceive of ethnicity in ways that do not comport with scholarly definitions. Indeed, around 1.5% of respondents provide answers such as "African" or the name of a sub-national region. The vast majority, however, choose ethnicities that appear in externally-imposed classifications, such as the Ethnic Power Relations data [@Vogt2015].

```{r ethnic}
library(xtable)
library(sjmisc)
load("/Users/david/Dropbox/Dissertation/Document/survey_chapter/survey_data/merged_afrobarometer.Rds") #built by afrobarometer_dataprep.R
options(xtable.comment = FALSE)
tab <- table(to_label(afro$eth_id))
tab2 <- cbind(tab, prop.table(tab)*100)
colnames(tab2) <- c("Count", "Percentage")
xtable(tab2, digits=c(0,0,1), caption="Summary of Ethnic Identification (waves 3-6)", label="tab:ethnic")
```

Relatively few respondents identify with their ethnic group, with 4.3% answering that they feel only an ethnic identity, and 7.4% saying that their ethnic identity was more prevalent than their national identity (see Table \@ref(tab:ethnic)). A plurality of respondents (35.8%) said that they felt equally attached to their national and ethnic identities, and a large percentage (34.1%) said that they feel only a national identity.


#### Political Participation {-}

Additionally, I examine the effects of repression on various forms of political participation, including voting[^vote], attending community meetings[^participation], protesting, and participating in violence. I collapse each variable into binary categories with individuals who engaged in the activity at least once coded as one, and individuals who did not participate in the activity for any reason coded as zero.

```{r partic}
options(xtable.comment = FALSE)
xtable(table(to_label(afro$vote)), caption="Voting")
```

### Independent Variables

### Individual-level Controls

### Country-level Controls

### The Model

[^vote]: Question text: "Understanding that some people were unable to vote in the most recent national election in [20xx], which of the following statements is true for you?" 0= You were not registered to vote, 1= You voted in the elections, 2= You decided not to vote, 3=You could not find the polling station , 4=You were prevented from voting, 5= You did not have time to vote, 6= You did not vote because you could not find your name in the voters’ register, 7= Did not vote for some other reason, 8= You were too young to vote, 9= Don't Know/ Can't Remember

[^participation]: The meeting, protest, and violence questions share a common stub. Question text: "Here is a list of actions that people sometimes take as citizens when they are dissatisfied with government performance. For each of these, please tell me whether you, personally, have done any of these things during the past year. If not, would you do this if you had the chance: Participated in a demonstration or protest march / Attended a community meeting / Used force or violence for a political cause." Possible responses: : 0=No, would never do this, 1=No, but would do if had the chance, 2=Yes, once or twice, 3=Yes, several times, 4=Yes, often, 9=Don’t know, 98=Refused to answer, -1=Missing 
