## Political Participation Results

The political participation results are reported in Table \@ref(tab:partic). Consistent with *H1*, repression at the individual level is associated with an increased probability that a respondent has engaged in violence, or is willing to do so. The effect is substantively large (substantive effects are discussed at length below) and statistically significant. Neither the individual-level threat of violence, nor the country-level degree of respect for human rights significantly influences violent mobilization. Collectively these results suggest that the presence of violence does not generally make individuals more willing to engage in violence themselves. Experiencing violence personally, however, produces such a drastic change in one's outlook that they are likely to increase their own willingness to engage in violence.

It is possible, however, that this result is endogenous. The Afrobarometer is not a panel survey, meaning that I am unable to track individuals over time. I therefore cannot determine whether attitudes toward the use of violence change in response to repression, or whether such attitudes might predate being attacked. It could be that individuals experience violence *because* they have engaged in violence themselves. Such individuals might be especially likely to be targeted with repression by the government. Furthermore, if individuals have engaged in violence, perhaps as members of a rebel group or in a riot, there is a strong possibility that their opponent will have fought back, leading the individual to report being attacked in the survey. I address this concern in two ways. First, later in the section I use the method of moments technique proposed by @Kim2007 to address endogeneity statistically. Second, that the potential for endogeneity should be substantially lower among individuals who are willing to, but have not yet engaged in violence. Identifying insurgents who intermix with the civilian population is immensely challenging for governments [@Kalyvas2006]. Thus if the effect of repression on attitudes towards violence is endogenous, we might expect a weak or non-existent relationship between repression and the willingness to use violence, as it would be difficult for the government to target such individuals. As Model 2 shows, this is somewhat true. The effect of repression on willingness to use violence is weaker than the effect on the actual use of violence. Yet, the effect is still relatively large and statistically significant, suggesting that the relationship matches my causal story in at least a portion of cases.

```{r hlm1}
library(lme4)
library(texreg)

load("/Users/david/Dropbox/Dissertation/Document/survey_chapter/survey_data/merged_afrobarometer.Rds")

h4 <- glmer(vote_recode ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic) + (1 | Year), data=afro, family=binomial("logit"), weights=withinwt)

h5 <- glmer(meeting_recode ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + primary + educ_recode + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic) + (1 | Year), data=afro, family=binomial("logit"), weights=withinwt)

h6 <- glmer(protest_recode ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic) + (1 | Year), data=afro, family=binomial("logit"), weights=withinwt)

h7 <- glmer(violence_recode ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic) + (1 | Year), data=afro, family=binomial("logit"), weights=withinwt)

h8 <- glmer(violence_willing ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic) + (1|Year), data=afro, family=binomial("logit"), weights=withinwt)

map <- list("latentmean"="Human Rights", "ethfrac"="Ethnolinguistic Fractionalization", "I(ethfrac^2)"="Ethnolinguistic Fractionalization$^{2}$", "polity2"="Polity", "civil1"="Civil War", "separatist1"="Separatist War", "attack_recode_bin1"="Attacked", "intim_recode_bin1"="Intimidated", "employment_recode1"="Employed", "primary1"="Primary Education", "urban_recode1"="Urban", "ruling_supporter1"="Ruling Party Supporter", "lage"="Age", "sex2"="Female")

texreg(list(h7, h8, h4,h5,h6), caption="Multilevel Models of Political Participation", custom.coef.map=map, custom.model.names=c("M1 Violence (Used)", "M2 Violence (Willing)", "M3 Voting", "M4 Meeting", "M5 Protest"), label="tab:partic")
```

I also examine the effects of repression on three other forms of political participation to shed light on alternative explanations. For example, it may be the case that violent individuals are simply very active in general, and thus have more opportunities than others to be repressed. Comparative homebodies might see lower rates of repression simply because they spend less time in public locations where repression tends to occur, and any apparent association with lower levels of political participation would likely be coincidental. In Model 2 I examine voting. Repression measured at the individual level has a negative relationship with voting. Individuals who reported an attack on themselves or a family member were 20.4% less likely than others to have voted. The threat of election-related violence has a smaller, but still statistically significant effect. At the national level better human rights practices are associated with higher baseline rates of voting, but the effect just misses the 90% level of statistical significance. These results suggest a potential explanation to the puzzle of why governments use repression despite the negative consequences I predict - it appears that repression is effective at deterring individuals from voting.



```{r partic_eff, fig.cap="Effect Plots for Violence (M4)"}
library(sjPlot)
library(ggplot2)
sjp.setTheme(base=theme_bw())

sjp.glmer(h7, type="eff", show.ci=T, title="")
```

## Ethnic Identification Results

```{r hlm2}
h1 <- glmer(eth_id_bin ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country), data=afro, family=binomial("logit"), weights=withinwt)

h2 <- glmer(eth_id_bin ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country / Ethnic), data=afro, family=binomial("logit"), weights=withinwt)

h3 <- glmer(eth_id_bin ~ latentmean + I(ethfrac^2) + ethfrac + polity2 + separatist + civil + attack_recode_bin + intim_recode_bin  + employment_recode + primary + urban_recode + ruling_supporter + lage + sex +  (1 | Country/Ethnic) + (1|Year), data=subset(afro, !is.na(Ethnic)), family=binomial("logit"), weights=withinwt)

texreg(list(h1,h2,h3), caption="Multilevel Models of Ethnic Identification", custom.coef.map=map, custom.model.names=c("M5", "M6", "M7"), label="tab:ethnic")
```
