## Use of Violence Results

The results for the use of  violence are reported in Table \@ref(tab:partic), Model 1. Consistent with *H1*, repression at the individual level is associated with an increased probability that a respondent has engaged in violence, or is willing to do so. The effect is substantively large, with the probability that an individual engaged in violence increasing by roughly 30%. As the baseline probability is quite low, the effect is small in absolute terms, moving from around 0.02 for individuals who have not been attacked, to 0.09 for individuals who have (see Figure \@ref(fig:violplot)). Furthermore, it is statistically significant at the 99.9% level. Neither the individual-level threat of violence, nor the country-level degree of respect for human rights significantly influences violent mobilization. Collectively these results suggest that the presence of violence does not generally make individuals more willing to engage in violence themselves. Experiencing violence personally, however, produces such a drastic change in one's outlook that they are likely to increase their own willingness to engage in violence.

It is possible, however, that this result is endogenous. The Afrobarometer is not a panel survey, meaning that I am unable to track individuals over time. I therefore cannot determine whether attitudes toward the use of violence change in response to repression, or whether such attitudes might predate being attacked. It could be that individuals experience violence *because* they have engaged in violence themselves. Such individuals might be especially likely to be targeted with repression by the government. Furthermore, if individuals have engaged in violence, perhaps as members of a rebel group or in a riot, there is a strong possibility that their opponent will have fought back, leading the individual to report being attacked in the survey. I argue, however, that the potential for endogeneity should be substantially lower among individuals who are willing to, but have not yet engaged in violence. Identifying insurgents who intermix with the civilian population is immensely challenging for governments [@Kalyvas2006]. Thus if the effect of repression on attitudes towards violence is endogenous, we might expect a weak or non-existent relationship between repression and the willingness to use violence, as it would be difficult for the government to target such individuals. As Model 2 shows, this is somewhat true. The effect of repression on willingness to use violence is weaker than the effect on the actual use of violence. Yet, the effect is still relatively large and statistically significant, suggesting that the relationship matches my causal story in at least a portion of cases.

```{r hlm1}
library(texreg)
library(lme4)

load("/Users/david/Dropbox/Dissertation/Document/survey_chapter/survey_data/merged_afrobarometer.Rds")
load("/Users/david/Dropbox/Dissertation/Document/survey_chapter/survey_data/survey_models.Rdata")

map <- list("(Intercept)"="(Intercept)","latentmean"="Human Rights", "ethfrac"="Ethnolinguistic Fractionalization", "I(ethfrac^2)"="Ethnolinguistic Fractionalization$^{2}$", "polity2"="Polity", "civil1"="Civil War", "separatist1"="Separatist War", "attack_recode_bin1"="Attacked", "intim_recode_bin1"="Intimidated", "employment_recode1"="Employed", "primary1"="Primary Education", "urban_recode1"="Urban", "ruling_supporter1"="Ruling Party Supporter", "lage"="Age", "sex2"="Female")

texreg(list(h7, h8), caption="Multilevel Models of Attitudes Toward Violence", custom.coef.map=map, custom.model.names=c("M1 Violence (Used)", "M2 Violence (Willing)"), label="tab:violence")
```

Perhaps due in part to its rarity, only a few control variables are significantly related to violence. Consistent with previous findings [e.g. @Humphreys2008], women are less likely than men to engage in violence, and are less likely to report a willingness to use violence. Individuals with at least a primary school education are slightly more likely than others to participate in violence, perhaps reflecting the fact that student organizations generally account for a substantial portion of political violence. This pattern does not hold for willingness to use violence, however. Urban individuals are less likely to be willing to use violence, while the measure is unrelated to the use of violence. Finally, willingness to use violence declines with age, while participation in violence is unrelated to age.

```{r violplot, fig.cap="Predicted Probability of the Use of Violence (Model 1)"}
library(sjPlot)
library(ggplot2)
library(sjmisc)
sjp.setTheme(base=theme_bw())

sjp.glmer(h7, type="pred", show.ci=T, title="", vars="attack_recode_bin", show.scatter=F, axis.lim=c(0,.6))
```

I also examine the effects of repression on three other forms of political participation to shed light on alternative explanations. For example, it may be the case that violent individuals are simply very active in general, and thus have more opportunities than others to be repressed. Comparative homebodies might see lower rates of repression simply because they spend less time in public locations where repression tends to occur, and any apparent association with lower levels of political participation would likely be coincidental. In Model 3 I examine voting. Repression measured at the individual level has a negative relationship with voting. Individuals who reported an attack on themselves or a family member were 20.4% less likely than others to have voted. The threat of election-related violence has a smaller, but still statistically significant effect. At the national level better human rights practices are associated with higher baseline rates of voting, but the effect just misses the 90% level of statistical significance. These results suggest a potential explanation to the puzzle of why governments use repression despite the negative consequences I predict - it appears that repression is effective at deterring individuals from voting, or at convincing them that politics is unlikely to address their needs. For two more involved forms of political action, however, attacks are associated with increased levels of political participation. Experiencing an attack is associated with a statistically significant, though substantively modest increase in the probability than an individual has participated in community meetings, as is the country-level human rights situation. The country-level measure is not significantly related to protest activity, but being attacked once again is, with individuals who have experienced an attack being more than twice as likely to have participated in protest. It should be noted, however, that the same endogeneity concerns that exist for violence apply to these forms of participation as well, as these results are consistent

```{r hlm 2}
texreg(list(h4,h5,h6), caption="Multilevel Models of Political Participation", custom.coef.map=map, custom.model.names=c("M3 Voting", "M4 Meeting", "M5 Protest"), label="tab:partic")
```

These results are robust to a number of adjustments. Changing the cutpoints for the variables that I collapse into binary measures does not substantially alter the results. Adding the additional controls mentioned in the research design does not alter the performance of my variables of interest, nor does removing any control variables. As mentioned in the research design section, I also explore the effects of several additional control variables. The results are also robust to the inclusion of random effects for the year in which the survey was administered and the survey wave, and including these factors as fixed effects rather than random results in only slight changes to the magnitude of the relationships.

Collectively, these results allow me to reject the null hypothesis of no relationship between repression and willingness to engage in violence associated with *H1*. Individuals who have been attacked are more than three times more likely than others to engage in violence, and roughly 20% more likely to express a willingness to use violence. The country-level human rights measure is not significantly related to either outcome, however, suggesting that the effect of repression is specific to the individuals who are targeted, and does not produce a widespread spillover effect leading large swaths of society to change their behavior. Several caveats must be noted, however. First, the repression measure is imprecise, as individuals who experienced violence personally are grouped with individuals with family members who experienced violence, and the actor who perpetrated the attack is not specified. Second, these results could be endogenous, with individuals being attacked because they used or were known to be willing to use violence. I address this possibility in Section \@ref(causal).

## Ethnic Identification Results

The ethnic identification results are reported in Table \@ref(tab:ethnic). Model 5 includes a random intercept for each country, while Model 6 adds an intercept for each ethnic group nested within each country, and to that Model 7 adds a random intercept for year.^[I use year instead of survey wave as the country-level variables are measured in yearly intervals.] In all three models, individuals who have experienced an attack are more likely to identify with their ethnic group than their nation, relative to individuals who have not experienced an attack. This effect size is equivalent to a roughly 42% increase, a change in probability from 0.12 to 0.17 (see Figure \@ref(fig:ethplot1)), but is statistically significant at the 99.9% level. Political intimidation has a similar effect. The country-level human rights measure is statistically significant in Models 5 and 6, with a similar substantive effect. Among the most repressive cases in the sample, individuals have a roughly 0.15 probability of identifying with their ethnic group, with the probability decreasing to 0.10 among the cases with the greatest respect for human rights (see Figure \@ref(fig:ethplot2)). The human rights variable is not significant in Model 7, likely because as a relatively constant measure, it has little ability to predict intercepts that vary by year.

```{r hlm3}
texreg(list(h1,h2,h3), caption="Multilevel Models of Ethnic Identification", custom.coef.map=map, custom.model.names=c("M5", "M6", "M7"), label="tab:ethnic")
```

The control variables provide a number of interesting results. As I expected, ethnolinguistic fractionalization has a substantively strong and statistically significant curvilinear relationship with ethnic identification in Models 5 and 7, and a linear one in Model 6 (indicated by the squared term not being statistically significant). The curvilinear pattern is consistent with my expectation that ethnic identification will be unlikely at extreme levels of diversity. Consistent with the findings of @Eifert2010, Models 5 and 6 show that the probability of ethnic identification increases as a country becomes more democratic. Countries experiencing civil war have a somewhat higher baseline level of ethnic identification, and the effect is considerable for separatist wars. At the individual level, urban-dwellers, ruling party supporters, and employed individuals are less likely to emphasize an ethnic identity. Having at least a primary education increases the probability that an individual with identify ethnically, and women are slightly more likely than men to adopt such an identity.

```{r ethplot1, fig.cap="Predicted Probability of Ethnic Identification (Model 5)"}
sjp.setTheme(base=theme_bw())
sjp.glmer(h1, type="pred", show.ci=T, title="", vars="attack_recode_bin", show.scatter=F, axis.lim=c(0,.6))
```

```{r ethplot2, fig.cap="Predicted Probability of Ethnic Identification (Model 5)"}
sjp.setTheme(base=theme_bw())
sjp.glmer(h1, type="pred", show.ci=T, title="", vars="latentmean", show.scatter=F, axis.lim=c(0,.6))
```

While further analysis is need to establish the direction of the causal relationship, these results do allow me to tentatively reject the null hypothesis of no relationship between repression and ethnic identification associated with *H2*. Individuals who have been attacked are more than 40% more likely than others to identify with their ethnic group. The country-level human rights measure tells a similar story, with the probability of ethnic identification being lower in countries with greater respect for human rights. As is the case with the violence results, I cannot here rule out the possibility of endogeneity. It is quite plausible that individuals who identify strongly with an ethnic group are most likely to be targeted with repression. Many governments repress ethnic minorities to prevent them from undermining national unity. For example, the Turkish government has denied the claim that the Kurds are a distinct ethnicity from Turks, and have repressed them to prevent a secessionist movement. I address the concern in the following section.
