## Alliance Formation Results

The alliance formation results are reported in Table \@ref(tab:alliance). Model 1  uses mono-ethnic alliances as the dependent variable, while Model 2 focuses on multi-ethnic alliances and Model 3 combines all alliances. In *H9* I predict that the probability of new ethnically homogeneous alliance will be greater following increases in repression. Consistent with this prediction, the "Change in Human Rights" variable has a strong negative relationship with the probability of new rebel group formation. A one-unit decrease in human rights (again, roughly the difference between France and Russia in recent years) more than triples the odds of a new rebel group forming. In the years following the largest declines in human rights practices (-2.5), the probability of a new mono-ethnic alliance is 0.21 (see Figure \@ref(fig:zeligplot)). When the change is zero or positive, the probability of such an alliance is around 0.01. This relationship is statistically significant at the 90% level. Given that the sample size is not especially small (n=1209), an $\alpha$ of 0.1 might be considered overly permissive. However, no other variable is significant at even the 90% level, suggesting that even after applying the rare events correction the model has limited statistical power. Thus, I contend that it is reasonable to interpret relationships at this significance level, and reject the null hypothesis of no relationship between repression and the emergence of mono-ethnic rebel groups.

```{r alliance}
library(lmtest)
library(plm)
library(texreg)
library(sjmisc)
library(Zelig, quietly=T)

country.year <- read.csv("~/Dropbox/Dissertation/Document/entry_chapter/entry_analysis/conflict_year.csv")

country.year$multireb <- ifelse(country.year$lagged_rebels>1, 1, 0)

country.year$latentmean_diff <- set_label(country.year$latentmean_diff, "Change in Human Rights")
country.year$new.alliance <- set_label(country.year$new.alliance, "New Rebel Group")

country.year$GWNoA <- as.factor(country.year$GWNoA)
country.year$yearf <- as.factor(country.year$Year)

# m1 <- glm(new.mono.alliance ~ latentmean_diff, data=data.frame(country.year), family=binomial("logit"))
# m1c <- coeftest(m1, vcov. = vcovHC(m1, type="HC1", cluster="GWNoA"))

m2 <- zelig(new.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m2c <- coeftest(m2, vcov. = vcovHC(m2, type="HC1", cluster="GWNoA"))

m3 <- zelig(new.multi.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m3c <- coeftest(m3, vcov. = vcovHC(m3, type="HC1", cluster="GWNoA"))

m4 <- zelig(new.mono.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m4c <- coeftest(m4, vcov. = vcovHC(m4, type="HC1", cluster="GWNoA"))

map <- list("(Intercept)"="(Intercept)","latentmean_diff" = "Change in Human Rights", "ethfrac" = "Ethnolinguistic Fractionalization", "latentmean_diff:ethfrac"="Human Rights X Fractionalization","country_ethnic"="Ethnic Groups", "maxint" = "Intensity Level", "new_conflict" = "New Conflict", "multireb"="Prev. Multi-rebel", "cont_civil" = "Contiguous Civil War", "lagged_rebels" = "Lagged Rebel Groups", "Incompatibilityterritory" = "Secessionist", "lgdp" = "Logged GDP per capita",  "lpop" = "Logged Population", "polity2" = "Polity", "postcw"="Post Cold War")

texreg(list(m4, m3, m2), caption="Rare Events Logit Models of Alliance Formation", custom.coef.map=map, custom.model.names = c("M1 Mono-ethnic", "M2 Multi-ethnic", "M3 All"), stars = c(0.001, 0.01, 0.05, 0.1), symbol="\\dagger", label="tab:alliance")
```

In Model 2 I do not find support for *H10*, as the relationship between "Change in Human Rights" and the probability of new multi-ethnic alliances does not approach statistical significance. While repression does not seem to deter this type of alliance as I expected, neither does it make them more likely. Thus while I find that repression is associated with a general increase in the probability of new alliances, the relationship seems to be driven by ethnically-homogeneous coalitions. The effect of repression seems to be specific to this type of alliance, rather than producing a general increase in the propensity to form coalitions.

```{r zeligplot, fig.cap="Predicted Probability of Mono-ethnic Alliance (Model 1)"}
x4 <- setx(m4, latentmean_diff= -2.5:1.5)
s4 <- sim(m4, x=x4)
plot(s4, xlab="Change in Human Rights", ylab="Predicted Probability", xlim=c(-3,2))
```

The only statistically significant control variable in any of the three models is logged GDP per capita in Model 3. The relationship is negative, indicating that alliances are less common in wealthier countries. One possible explanation is that the variable is acting as a proxy for the intensity or spread of the conflict, capturing an attribute distinct from the binary measure of whether the conflict produced 1,000 fatalities. In cases such as Afghanistan where most of the country is consumed by war, the economy is likely to suffer. In cases where the fighting is more localized, such as Ukraine in recent years, there will not necessarily be a significant economic decline at the country level. The former situation might be more likely to have a plethora of rebel groups available to form alliances.

The findings in this section are broadly consistent with my theoretical framework. Increased repression is associated with higher probabilities of the formation of ethnically homogeneous alliances, which supports my expectation that repression triggers a cycle of realignment around ethnic identity. One case that is consistent with this story is the Uganda National Liberation Front. Uganda is among the most ethnically diverse societies on earth, with an ethnolinguistic fractionalization score indicating that there is nearly a 90% chance that two randomly selected individuals will be from different ethnic groups. A number of small rebel groups formed there in 1978 with the goal of overthrowing Idi Amin, to which the government responded with a substantial increase in repression (a change of -0.5 in the Latent Human Protection Scores). In early 1979, with help from the Tanzanian government, several ethnically Lango rebel groups responded by a forming an alliance, the Uganda National Liberation Front. A month later they successfully overthrew Amin. While numerous small rebel groups were active during this time [@Lewis2016], only the bloc of Lango groups was able to successfully form an alliance.
