## Alliance Formation Results

The alliance formation results are reported in Table \@ref(tab:alliance). Model 4  uses mono-ethnic alliances as the dependent variable, while Model 5 focuses on multi-ethnic alliances and Model 6 combines all alliances. In *H9* I predict that the probability of new ethnically homogeneous alliance will be greater following increases in repression. Consistent with this prediction, the "Change in Human Rights" variable has a strong negative relationship with the probability of new rebel group formation. A one-unit decrease in human rights (again, roughly the difference between France and Russia in recent years) more than triples the odds of a new rebel group forming. In the years following the largest declines in human rights practices (-2.5), the probability of a new mono-ethnic alliance is 0.21 (see Figure \@ref(fig:zeligplot)). When the change is zero or positive, the probability of such an alliance is around 0.01. This relationship is statistically significant at the 90% level. Given that the sample size is not especially small (n=1209), an $\alpha$ of 0.1 might be considered overly permissive. However, no other variable is significant at even the 90% level, suggesting that even after applying the rare events correction the model has limited statistical power. Thus, I contend that it is reasonable to interpret relationships at this significance level, and reject the null hypothesis of no relationship between repression and the emergence of mono-ethnic rebel groups.

```{r alliance}
library(lmtest)
library(plm)
library(texreg)
library(sjmisc)
library(Zelig, quietly=T)

country.year <- read.csv("~/Dropbox/Dissertation/Document/entry_chapter/entry_analysis/conflict_year.csv")

country.year$multireb <- ifelse(country.year$lagged_rebels>1, 1, 0)

country.year$latentmean_diff <- set_label(country.year$latentmean_diff, "Change in Human Rights")
country.year$new.alliance <- set_label(country.year$new.alliance, "New Rebel Group")

country.year$GWNoA <- as.factor(country.year$GWNoA)
country.year$yearf <- as.factor(country.year$Year)

# m1 <- glm(new.mono.alliance ~ latentmean_diff, data=data.frame(country.year), family=binomial("logit"))
# m1c <- coeftest(m1, vcov. = vcovHC(m1, type="HC1", cluster="GWNoA"))

m2 <- zelig(new.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m2c <- coeftest(m2, vcov. = vcovHC(m2, type="HC1", cluster="GWNoA"))

m3 <- zelig(new.multi.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m3c <- coeftest(m3, vcov. = vcovHC(m3, type="HC1", cluster="GWNoA"))

m4 <- zelig(new.mono.alliance ~ latentmean_diff + ethfrac  + maxint + cont_civil + multireb + lgdp + lpop + mtnest + polity2, data=data.frame(country.year), model="relogit", cite=F)
#m4c <- coeftest(m4, vcov. = vcovHC(m4, type="HC1", cluster="GWNoA"))

map <- list("(Intercept)"="(Intercept)","latentmean_diff" = "Change in Human Rights", "ethfrac" = "Ethnolinguistic Fractionalization", "latentmean_diff:ethfrac"="Human Rights X Fractionalization","country_ethnic"="Ethnic Groups", "maxint" = "Intensity Level", "new_conflict" = "New Conflict", "multireb"="Prev. Multi-rebel", "cont_civil" = "Contiguous Civil War", "lagged_rebels" = "Lagged Rebel Groups", "Incompatibilityterritory" = "Secessionist", "lgdp" = "Logged GDP per capita",  "lpop" = "Logged Population", "polity2" = "Polity", "postcw"="Post Cold War")

texreg(list(m4, m3, m2), caption="Rare Events Logit Models of Alliance Formation", custom.coef.map=map, custom.model.names = c("M4 Mono-ethnic", "M5 Multi-ethnic", "M6 All"), stars = c(0.001, 0.01, 0.05, 0.1), symbol="\\dagger", label="tab:alliance")
```

In Model 5 I do not find support for *H10*, as the relationship between "Change in Human Rights" and the probability of new multi-ethnic alliances does not approach statistical significance. While repression does not seem to deter this type of alliance as I expected, neither does it make them more likely. Thus while I find that repression is associated with a general increase in the probability of new alliances, the relationship seems to be driven by ethnically-homogeneous coalitions. The effect of repression seems to be specific to this type of alliance, rather than producing a general increase in the propensity to form coalitions. Disaggregating the results by conflict intensity reveals that the findings are primarily driven by less severe conflicts, as the results hold for conflict-years with fewer than 1,000 fatalities, but not for those with greater than 1,000 (see Tables \@ref(tab:alliance-conflict) and \@ref(tab:alliance-war) in the Chapter 5 Appendix). The result for mono-ethnic alliances holds among conflicts over the central government, but not among secessionist conflicts. The combined alliance formation result holds in neither subsample (see Tables \@ref(tab:alliance-gov) and \@ref(tab:alliance-sec)). As is the case in previous analyses, my hypotheses perform best in lower-intensity government conflicts. One explanation for the intensity result is that forming alliances requires an opportunity for rebel elites to meet and negotiate a merger, which is unlikely to occur during periods of intense fighting. The conflict type results again suggests that secessionist movements tend to be unified around ethnic identity from the outset, and thus have less need to engage in realignment.

```{r zeligplot, fig.cap="Predicted Probability of Mono-ethnic Alliance (Model 1)"}
x4 <- setx(m4, latentmean_diff= -2.5:1.5)
s4 <- sim(m4, x=x4)
plot(s4, xlab="Change in Human Rights", ylab="Predicted Probability", xlim=c(-3,2))
```

The only statistically significant control variable in any of the three models is logged GDP per capita in Model 3. The relationship is negative, indicating that alliances are less common in wealthier countries. One possible explanation is that the variable is acting as a proxy for the intensity or spread of the conflict, capturing an attribute distinct from the binary measure of whether the conflict produced 1,000 fatalities. In cases such as Afghanistan where most of the country is consumed by war, the economy is likely to suffer. In cases where the fighting is more localized, such as Ukraine in recent years, there will not necessarily be a significant economic decline at the country level. The former situation might be more likely to have a plethora of rebel groups available to form alliances.

The findings in this section are broadly consistent with my theoretical framework. Increased repression is associated with higher probabilities of the formation of ethnically homogeneous alliances, which supports my expectation that repression triggers a cycle of realignment around ethnic identity. One case that is consistent with this story is the Uganda National Liberation Front. Uganda is among the most ethnically diverse societies on earth, with an ethnolinguistic fractionalization score indicating that there is nearly a 90% chance that two randomly selected individuals will be from different ethnic groups. A number of small rebel groups formed there in 1978 with the goal of overthrowing Idi Amin, to which the government responded with a substantial increase in repression (a change of -0.5 in the Latent Human Protection Scores). In early 1979, with help from the Tanzanian government, several ethnically Lango rebel groups responded by a forming an alliance, the Uganda National Liberation Front. A month later they successfully overthrew Amin. While numerous small rebel groups were active during this time [@Lewis2016], only the bloc of Lango groups was able to successfully form an alliance.

## Combining the Processes

This project is motivated by a desire to explain variation in the number of rebel groups across and within conflicts. To this point, I have examined individually three processes that increase or decrease the number of rebel groups. Doing this has allowed me to discuss very specific causal processes. Yet examining each process separately does not allow me to speak to the total number of rebel groups we should expect at various levels of repression. It is not clear, for example, to what extent alliances offset the increases to the number of rebel groups brought by splintering. As a final quantitative analysis, I combine group formation, splintering, and alliance formation and model the probability that there will be multiple rebel groups active in a conflict-year. To do this I fit a logistic regression model with a binary indicator of whether there were at least two rebel groups present in a conflict year.^[A count model such as Poisson regression would not be appropriate here, as rebel groups can persist across time periods, violating the assumption of independent counts in each period.] The unit of analysis is again the conflict-year, and the controls are each described in the research design for the alliance analysis.

```{r combined}
library(sjmisc)

country.year$lmtnest <- log(country.year$mtnest+1)
country.year$democ <- ifelse(country.year$polity2 > 5, 1, 0)
country.year$multirebdv <- ifelse(country.year$n_rebels>1, 1, 0)

country.year$latentmean <- set_label(country.year$latentmean, "Human Rights")
country.year$latentmean_diff <- set_label(country.year$latentmean_diff, "Change in Human Rights")
country.year$multirebdv <- set_label(country.year$multirebdv, "Muliple Rebel Groups")

c1 <- glm(multirebdv ~ multireb + latentmean_diff + ethfrac  + maxint + cont_civil + lgdp + lpop + larea + lmtnest + democ + postcw, data=data.frame(country.year), family=binomial("logit"))
c1c <- coeftest(c1, vcov. = vcovHC(c1, type="HC1", cluster="GWNoA"))

c2 <- glm(multirebdv ~ multireb + latentmean_diff + ethfrac + I(ethfrac^2) + maxint + cont_civil + lgdp + lpop + larea + lmtnest + democ + postcw, data=data.frame(country.year), family=binomial("logit"))
c2c <- coeftest(c2, vcov. = vcovHC(c2, type="HC1", cluster="GWNoA"))

c3 <- glm(multirebdv ~ multireb + latentmean + ethfrac + I(ethfrac^2) + maxint + cont_civil + lgdp + lpop + larea + lmtnest + democ + postcw, data=data.frame(country.year), family=binomial("logit"))

map2 <- list("(Intercept)"="(Intercept)","latentmean_diff" = "Change in Human Rights", "latentmean"="Human Rights","lagged_rebels > 1TRUE"="Prev. Multi-rebel","ethfrac" = "Ethnolinguistic Fractionalization", "I(ethfrac^2)"="Ethnolinguistic Fractionalization$^{2}$","latentmean_diff:ethfrac"="Human Rights X Fractionalization","country_ethnic"="Ethnic Groups", "maxint" = "Intensity Level", "new_conflict" = "New Conflict", "multireb"="Prev. Multi-rebel", "cont_civil" = "Contiguous Civil War", "lagged_rebels" = "Lagged Rebel Groups", "Incompatibilityterritory" = "Secessionist", "lgdp" = "Logged GDP per capita",  "lpop" = "Logged Population", "larea"="Logged Area", "log(mtnest + 1)"="Logged Mountainous Terrain", "polity2 > 5TRUE" = "Democracy", "postcw"="Post Cold War")

texreg(list(c1,c2,c3), custom.coef.map=map2, custom.model.names=c("M7","M8","M9"), caption="Logit Models of Multi-Rebel Conflict-Years", label="tab:combined")
```

The combined results are reported in Table \@ref(tab:combined). The "Change in Human Rights" measure has a strong negative relationship with the probability of multiple rebel groups (Models 7 and 8). As human rights improve, the probability that a conflict-year will have multiple rebel groups decreases. As a country becomes more repressive, the probability of multiple rebel groups increases. The relationship is statistically significant in both models, and the effect size is large. A two standard deviation change in human rights (-0.486) changes the probability from roughly 0.19 to 0.26, a 37% increase (see Figure \@ref(fig:combinedplot)). Model 9 includes the absolute value of the human rights measure, rather than the change. It too is statistically significant. At the highest observed levels of repression the probability of multiple rebel groups is roughly 0.46. At the mean value for the sample (-1.24) the probability is 0.14 (see Figure \@ref(fig:combinedplot2)). Both the absolute value and change in repression are thus strong predictors of whether a conflict will have multiple rebel groups.

```{r combinedplot, fig.cap="Predicted Probability of Multiple Rebel Groups", cache=F}
library(sjPlot)
library(ggplot2)
set_theme(base=theme_bw())

sjp.glm(c2, type="pred", vars=("latentmean_diff"), show.ci=T, title="", show.scatter = F, axis.lim = c(0, 1))
```

As is the case in previous analyses, the results hold among conflict-years with less than 1,000 battle-related deaths, but not among those with greater than 1,000 (see Tables \@ref(tab:combined-conflict) and \@ref(tab:combined-war) in the Chapter 5 Appendix). This may be the result of the relatively small number of war-years in the latter category (n=280). Indeed, only the "Previously Multi-Rebel" measure is statistically-significant in the war subsample. Also consistent with previous analyses is the fact that the results appear to be primarily driven by conflicts over the central government, as the findings in that subsample match closely with the aggregate patterns. Among secessionist conflicts the "Change in Human Rights" measure is not statistically significant, though the absolute level of human rights (used in Model 9) is. Thus repression is associated with greater numbers of rebel groups in both secessionist and non-secessionist conflicts, but only explains the timing of new rebel group formation in the non-secessionist sample (see Tables \@ref(tab:combined-gov) and \@ref(tab:combined-sec)). As was the case for the individual processes, the aggregate results suggest that the relationship between repression and the number of rebel groups is strongest among less intense conflicts over the central government. 

Only a few control variables are statistically significant. The strongest predictor in each model, however, is the lagged dependent variable ("Previously Multi-Rebel"). Once a conflict has multiple rebel groups that arrangement is likely to persist for at least one year. This suggest that the presence of multiple rebel groups is not simply a case of two groups briefly overlapping, before one replaces the other. Interestingly, the contiguous civil war measure is statistically significant, but negative in models 7 and 8. One possible explanation is that rebel groups often seek refuge across international borders, especially when neighboring states are weak, as they would be during a civil war [@salehyan07]. Ethnolinguistic fractionalization is not statistically significant as a linear effect, but a curvilinear effect is significant (Model 8). In this case it is a U-shaped relationship, with the probability of multiple rebel groups being highest and high and low values of ethnic diversity.

```{r combinedplot2, fig.cap="Predicted Probability of Multiple Rebel Groups", cache=F}
sjp.glm(c3, type="pred", vars=("latentmean"), show.ci=T, title="", show.scatter = F, axis.lim = c(0, 1))
```

In short, repression is a strong predictor for the presence of multiple rebel groups. This is perhaps unsurprising given that while all three outcomes are rare, new group formation and splintering combined are more common than alliance formation. My theory has the ability not only to explain each of these processes individually, but provides a strong explanation for the overall structure of the rebel movement.
