---
title: 'Late to the Party: Why Do New Rebel Groups Join Civil Conflicts?'
author: "David Bowden"
date: "4/14/2017"
output: 
  beamer_presentation:
    theme: "Rochester"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F)
```

## Introduction

- Why do some civil wars have multiple rebel groups?
- Multi rebel conflicts among deadliest, long-lasting, most prone to recurrence
- Some lit on fragmentation, but little on entry of new groups

## Theory

- Entry of new groups requires improved relative cost/benefit of fighting
    - People who previously decided it was not in their interest to fight must change their mind
- Entry also requires division w/ other dissidents
    - People who decide to mobilize must decide to create a new group rather than joining an existing one
        
## Costs and Benefits

- Benefits of fighting can increase during conflict
- Costs of non-violence can also increase
    - If non-violent people are at risk of violence, free riding isn't very free (Kalyvas and Kocher 2007)
    - As risk associated with non-violence approaches risk associated with participation in violence, relative cost of fighting decreases
    - Repression of civilians should produce this outcome
    
    
## Divisions Among Dissidents

- Individuals have many potential identities, and choose which to emphasize for instrumental reasons (Posner 2005, Penn 2008)
- Repression can influence identity choice
- Indiscriminate repression might activate broad, inclusive identities
    - Unified dissident movement
- Discriminatory repression activates identites that are basis for repression (ethnicity, religion)
    - More divided dissident movement
        
## Hypotheses

- Hypothesis 1: The number of rebel groups in a country should increase with the level of repression
- Hypothesis 2: The number of rebel groups should increase with the extent to which repression is targeted
- Hypothesis 3: There should be a positive interaction between repression and discrimination

## Research Design

- DV: Active rebel groups per country-year, 1946-2015 (UCDP)
- IV1: Latent Human Protection Scores (Fariss 2014)
- IV2: % of population not facing discrimination according to EPR (Vogt et al 2015)
- Controls: conflict intensity, # UCDP conflicts, % UCDP conflicts over territory, ethnolinguistic fractionalization, population, GDPpc, contiguous civil wars
- Not Shown: Polity, mountainous terrain, oil revenues, strength of largest rebel group, centralization of largest rebel group, external support for rebels
- Model: Poisson regression w/ fixed effects for country


## Results

```{r, results='asis'}
library(lmtest)
library(plm)
library(texreg)

load("~/Dropbox/Dissertation/Analyses/epr_group_formation/country_year.Rdata")

m1 <- glm(n_rebels ~ log(rgdppc) + repression_lag + discrimination_lag + ethfrac + n_conflicts +  (cont_civil>0) + IntensityLevel + pcterr + log(pop) + GWNoA, data=country_year, family="poisson")
m1c <- coeftest(m1, vcov. = vcovHC(m1, type="HC0", cluster="GWNoA"))

m2 <- glm(n_rebels ~ log(rgdppc) + repression_lag*discrimination_lag + ethfrac + n_conflicts +  (cont_civil>0) + IntensityLevel + pcterr + log(pop) + GWNoA, data=country_year, family="poisson")
m2c <- coeftest(m2, vcov. = vcovHC(m2, type="HC0", cluster="GWNoA"))

plotreg(m1c, omit.coef = "GWNoA")
```

## Results

```{r}
library(sjPlot)
library(ggplot2)
set_theme(base=theme_bw())

sjp.glm(m1, type="eff", vars=c("repression_lag"), show.ci=T, title="")
```

## Results

```{r}
library(sjPlot)
library(ggplot2)
set_theme(base=theme_bw())

sjp.glm(m1, type="eff", vars=c("discrimination_lag"), show.ci=T, title="")
```

## Results

```{r}
plotreg(m2c, omit.coef="GWNoA")
```

## Results

```{r}
sjp.int(m2, type="eff", show.ci=T, mdrt.values = "minmax", axis.title = "Discrimination", legend.labels = c("Min Human Rights", "Max Human Rights"), legend.title = "", title = "")
```

## Discussion

- Repression associated with a large, statistically significant increase in number of rebel groups
- Discrimination associated with smaller, but also significant increase
- Interaction of repression and discrimination signficant - effect of repression increases with level of discrimination

## Conclusion

- Rebel cohesion depends on which identities are activated
- The government can play an important role in shaping structure of rebel movements
- Methodological improvements: better measure of targeted repression, instrument
- Future work: government strategy, relationship between original and joining rebel groups